---
title: "Homework4"
author: "Yuxin"
date: "2018.11.6"
output: github_document
---


```{r setup, include=FALSE}
library(tidyverse)
library(stringr)
library(purrr)
```

# Problem 1 

This zip file contains data from a longitudinal study that included a control arm and an experimental arm. Data for each participant is included in a separate file, and file names include the subject ID and arm.

## Quesiton 1.1

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

* Start with a dataframe containing all file names; the list.files function will help
* Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
* Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary

```{r}
## Write a function to read all data 
file_name = list.files("./data")
read_function = function(file_name){
 study_data = read_csv(file = str_c("./data/",file_name)) %>%
   mutate(file = file_name)
}

## Use function to read all datasets and tidying the dataframe
study_data = 
  map_df(file_name, read_function) %>%
  gather(key = week, value = observation, week_1:week_8) %>%
  separate(file, into = c("group", "subject"), sep = "_") %>%
  mutate(group = recode(group, con = "control", exp = "experiment"),
         subject = str_remove(subject,".csv"),
          week = str_remove(week, "week_"))

```

## Quesiton 1.2

Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r}
ggplot(study_data, aes(x = week, y = observation, group = subject, color = subject))+
  geom_line()+
  facet_grid(.~group)+
  labs(title = "Observations over time of two different groups")
```

From the plot, we can observe that the subjects in control arm are constant over eight weeks. However, the subjects in experiment arm are increasing over time. Moreover, the subjects in the Experimental group potentially have larger observation value than the Control group. We may need more formal statistical inference to conclude if there is a difference between groups.    

# Problem 2

The Washington Post has gathered data on homicides in 50 large U.S. cities and made the data available through a GitHub repository here. You can read their accompanying article here.


```{r}
## Read data from gtihub
url = "https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"
homicide_data = read.csv(url) %>%
  janitor::clean_names() %>%
as.tibble()
```

## Quesiton 2.1
Describe the raw data. Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

### Describe the raw data

This homicide dataset from The Washington Post contains 13 variables 52179 observations. Thirteen variables basically contain all information about a homicide event. For example, the victim first, victim last, victim age, sex contain the identification of the homicide victim. City, state, latitude, and longitude describe where the homicide happened. Uid, reported date and disposition give us more information of homicdie report. For variable "reported data," we observe two values "201511105" and "201511018". These values are abnormal as the date value and may be caused by typo error. Moreover, for the observation uid is "Pit-000050", it seems that someone combine victim_last and race into victim_last. This leads to a completely wrong observation. 

```{r}
## Create city_state variable
homicide_data = homicide_data %>%
  mutate(city_state = str_c(city, state, sep ="," ))
head(homicide_data,5)

## Summarize the number of homicides and number of unsolved homicides
homicide_summary = homicide_data %>%
  group_by(city_state) %>%
  mutate(total_homicides = n()) %>%
  filter(disposition == "Closed without arrest" | disposition == "Open/No arrest") %>%
  summarise(unsolved_homicides = n(),
            total_homicides = max(total_homicides))
homicide_summary %>%
  knitr::kable()
```

## Question 2.2
For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

```{r}
baltimore_data =  homicide_summary %>%
   filter(city_state == "Baltimore,MD") %>% 
   select(unsolved_homicides,total_homicides)

prop_test_result = prop.test(baltimore_data[[1]],baltimore_data[[2]]) %>%
  broom::tidy() %>%
  select(estimate,conf.low,conf.high) %>%
  rename("Estimated Proportion" = estimate,
         "Lower bound of Confidence Intervals" = conf.low,
         "Lower bound of Confidence Intervals" = conf.high) 
  prop_test_result %>%
  knitr::kable()
```

## Question 2.3
Now run prop.test for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of purrr::map, purrr::map2, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city.

```{r}
## Write a function to run prop.test
homicide_prop = function(df){
  homicide_prop_test = prop.test(df$unsolved_homicides, df$total_homicides) %>%
  broom:tidy() %>%
  select(estimate,conf.low,conf.high) %>%
  rename("Estimated Proportion" = estimate,
         "Lower bound of Confidence Intervals" = conf.low,
         "Lower bound of Confidence Intervals" = conf.high)
}






```